\documentclass{template}

\usepackage[square,numbers]{natbib}

\usepackage{hyperref,xcolor}
\hypersetup{linkcolor=blue}
\hypersetup{%
  citecolor=blue
}

\setname{Alexander Weichart}{}
\setaddress{Rüdigerstr. 5 Regensburg}
\setmobile{\getPhone}
\setmail{alexanderweichart@fastmail.com}
\setcitizenship{German}
\setlinkedinaccount{https://www.linkedin.com/in/alexander-weichart-a357241a4/} 
\setprojects{https://www.linkedin.com/in/alexander-weichart-a357241a4/details/projects/} 
\sethomepage{https://www.alexanderweichart.de/}
\setgithubaccount{https://github.com/AlexW00} 
\setthemecolor{Black}


\begin{document}

%Create header
\headerview
\vspace{1ex} % white space

%
\section{Skills}
    \newcommand{\skillone}{\createskill{Main Languages}{Java \cpshalf TypeScript }}
    \newcommand{\skilltwo}{\createskill{Main Technologies}{SpringBoot, React, PostgreSQL \cpshalf Kubernetes, GitLab, Flux CD \cpshalf OpenAI, LangChain \cpshalf Linux  }}
    %
    \createskills{\skillone, \skilltwo}
    \vspace{-3mm} % reduces whitespace!
    %
\bigskip

%
\section{Education} 
    \datedexperience{Bachelor of Arts - Media Computer Science (GPA: 3.5)}{Sep 2019 - Sep 2023}
    \explanation{University of Regensburg}{Regensburg, Germany}
    \explanationdetail{
        \smallskip
        \coloredbullet\ %
        \textbf{Core topics}: Full Stack Development, Agile Project Management, Natural Language Processing and Ethics.

        \smallskip
        \coloredbullet\ %
        Studied and applied the modern application tech stack used commonly in web-development.

        \smallskip 
        \coloredbullet\ %
        Acquired proficiency in agile user-centered software development through multiple group projects.
     }

\bigskip

\section{Experience}
    %
    \datedexperience{DEBTVISION GmbH (Baden-Württemberg State Bank)}{Jan 2025 - present}
    \explanation{Software Engineer - Java, SpringBoot, TypeScript, Kubernetes, GitLab}{Stuttgart, Germany}
    \explanationdetail{
    \smallskip
    \coloredbullet\ %
    \textbf{Core tasks:} Full-stack development on a financial platform, focusing on Backend and DevOps.

    \smallskip 
    \coloredbullet\ %
    Implemented highly automated tooling to restore the entire production environment as a separate recovery environment to a different cloud provider from scratch.
    
    \smallskip 
    \coloredbullet\ %
    Lead and oversaw the integration of AI-solutions into development processes.
    }
    %
    \datedexperience{DEBTVISION GmbH (Baden-Württemberg State Bank)}{Oct 2023 - Dec 2024}
    \explanation{Junior Software Engineer - Java, SpringBoot, TypeScript, Kubernetes, GitLab}{Stuttgart, Germany}
    \explanationdetail{
    \smallskip
    \coloredbullet\ %
    \textbf{Core tasks:} Full-stack development on a financial platform, focusing on Backend and DevOps.

    \smallskip 
    \coloredbullet\ %
    Test-driven development of multiple SpringBoot microservices in an agile environment.

    \smallskip 
    \coloredbullet\ %
    Optimized the development Kubernetes cluster, achieving a 100\% increase in CPU capacity and 12\% increase in RAM capacity, while reducing the monthly operational costs by 17\%.
    }
    %
    \datedexperience{University of Regensburg}{Sep 2020 - Sep 2023}
    \explanation{Student Research Assistant - JavaScript, Kotlin, C, Neo4J, Figma}{Regensburg, Germany}
    \explanationdetail{
    \smallskip
     \coloredbullet\ %
    \textbf{Core tasks:} Development of software for prototypes, studies and production deployments.
    
    \smallskip 
    \coloredbullet\ %
    Implemented an app to take native screenshots of a computer screen via smartphone camera.

    \smallskip 
    \coloredbullet\ %
    Architected a knowledge graph of course contents and implemented applications to interact with it.

    }

\bigskip

%
\section{Projects}
    %
    \datedexperience{TinyCompTS}{Dec 2021 - Mar 2022}
    \explanationdetail{
    \smallskip 
    \coloredbullet\ %
    Developed a compiler capable of lexing, parsing, and compiling code based on user-defined attribute grammars.

    \smallskip 
    \coloredbullet\ %
    Launched the project as an open-source NPM and Deno package, expanding its accessibility to a wider audience.
    
    \smallskip 
    }
    %
    \datedexperience{Beat Kanji}{Nov 2025 - Nov 2025}
    \explanationdetail{
    \smallskip 
    \coloredbullet\ %
    Developed and launched an iOS rhythm game to practice Japanese kanji characters.
    \smallskip 
    }
    %
    \datedexperience{Zeitgeist}{Aug 2025 - Nov 2025}
    \explanationdetail{
    \smallskip 
    \coloredbullet\ %
    Developed and launched an iOS app to privately take Instagram like Stories, but locally.
    \smallskip 
    }
    %
    \datedexperience{AI Experiments}{Mar 2022 - present}
    \explanationdetail{
    \smallskip 
    \coloredbullet\ %
    GPT-Lang: Prototyped a programming language to turn natural language into JavaScript.
    
    \smallskip 

    \coloredbullet\ %
    AI-HUD: MacOS app to detect Japanese text on screen and interact with it using a chat interface.
    
    \smallskip 
    
    \coloredbullet\ %
    Directory-Chat: Prototyped a web-app to chat with local directories.
}


\bigskip

\section{Extracurricular Activities}
\indent
\explanationdetail{
\smallskip 
\coloredbullet\ %
Maintainer of multiple popular open-source projects (\href{https://github.com/AlexW00}{GitHub})

\smallskip 
\coloredbullet\ %
Member at \href{https://ratisbona-coding.org/}{Ratisbona Coding E.V.}, an organization that organizes numerous coding-related events such as the annual "Hackaburg" Hackathon held in Regensburg, Germany.

\smallskip 
\coloredbullet\ %
Supporting member at the German-Japanese Society Regensburg (\href{https://djg-regensburg.de/de/}{DJG Regensburg})

\smallskip 
\coloredbullet\ %
Japanese language and culture

\smallskip 
\coloredbullet\ %
\textbf{Languages}: German (native), English (fluent), Japanese (N2-N3), French (basic), Latin (basic)
}
\bigskip

\section{Publications}
\indent
\explanationdetail{
\smallskip 
\coloredbullet\ %
Andreas S., Thomas F., Alexander W., Alexander H., and Raphael W., "ScreenshotMatcher: Taking Smartphone Photos to Capture Screenshots." \emph{MuC '21: Proceedings of Mensch und Computer 2021}, Ingolstadt Germany.
 }

\end{document}
